EBASE manuscript

### 2022-10-18 manu-draft.qmd
working on outline

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "EBASE manuscript"
bibliography: refs.bib
csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Jill M Arriola:
      email: jva5648@psu.edu 
      institute: [PSU]
      correspondence: false
  - Maria:
      email: mxh367@psu.edu
      institute: [PSU]
      correspondence: false
  - Raymond G Najjar:
      email: rgn1@psu.edu
      institute: [PSU]
      correspondence: false

@@

@@

@@

@@

\newpage

@@

\newpage

@@

\newpage

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "EBASE manuscript"
bibliography: refs.bib
csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Jill M Arriola:
      email: jva5648@psu.edu 
      institute: [PSU]
      correspondence: false
  - Maria Hermann:
      email: mxh367@psu.edu
      institute: [PSU]
      correspondence: false
  - Raymond G Najjar:
      email: rgn1@psu.edu
      institute: [PSU]
      correspondence: false

@@

* Overview of metabolism - importance
* Existing methods: Odum/WtRegDO, BASEmetab, references in @Grace15, applications to lakes and streams
* Applications to estuaries - challenges
* Goals and objectives

@@

* EBASE theory
* EBASE R package

@@

* Comparison with Odum and BASEmetab: Fwoxy Appalachicola
* Comparison with Odum and BASemetab: Apalachicola
* Sensitivity analyses:
     * optimization length
     * priors
* Application to representative NERR sites

@@

<!-- \newpage -->

@@

Figure 1: Fwoxy comparisons

Figure 2: Apalachicola comparisons

Figure 3: Sensitivity analyses

Figure 4: NERRS application

<!-- \newpage  -->

@@

Table 1: EBASE parameters and outputs

Table 2: Summary stats of Fwoxy comparison

Table 3: Summary stats of Apalachicola comparison

Table 4: Key parameters form NERRS application

<!-- \newpage -->
